---
title: "PsychxBiomed_BayesianAnalysis"
author: "H.L. Glandorf"
date: "2024-05-24"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Psych x Biomed Analysis: Bayesian Approach (Paper vers.; Exploratory analsis Part 3a)
This code file carries out the multilevel mediation analysis based on participants who completed at least two waves with Bayesian estimation and priors. The models here are using biomarkers as mediators simultaneously. 

These are the objectives:
- data preparation (e.g., scale the data, create long format, clean data)
- data imputation with multivariate imputation by chained equations (MICE)
- SD calculation for prior adjustment 
- multilevel mediation analyses with Bayesian estimator and priors for biomarkers as simultaneous mediators 
-- no information priors
-- priors based on previous research

# Load libraries
```{r libraries}
library(blavaan)
library(readxl)
library(broom)
library(tidyverse)
library(ggplot2)
library(semTools)
library(mice)
```

# Load data
```{r data loading}
dat <- read_csv("redframe.csv")
```

# Scaling
```{r scaling and outlier screening}
##add in time difference between time of saliva sample and time eaten
dat <- dat %>% mutate(t1timediff = t1time-t1timeeat,
               t2timediff = t2time-t2timeeat,
               t3timediff = t3time-t3timeeat)

##calculating z-scores
datz <- dat %>% 
  mutate(t1TB_z = scale(t1TB), 
         t1EXH_z = scale(t1EXH),
         t1DEV_z = scale(t1DEV),
         t1RSA_z = scale(t1RSA),
         t1PS_z = scale(t1PS),
         t1DS_z = scale(t1DS),
         t1PSQI_z = scale(t1PSQI),
         t1ISI_z = scale(t1ISI),
         t1iga_z = scale(t1iga_flow),
         t1testo_z = scale(t1test_conc),
         t1dheas_z = scale(t1dheas_flow),
         t1cort_z = scale(t1cort_conc),
         t1crp_z = scale(t1crp_conc),
         t1timediff_z = scale(t1timediff),
         t2TB_z = scale(t2TB), 
         t2EXH_z = scale(t2EXH),
         t2DEV_z = scale(t2DEV),
         t2RSA_z = scale(t2RSA),
         t2PS_z = scale(t2PS),
         t2DS_z = scale(t2DS),
         t2PSQI_z = scale(t2PSQI),
         t2ISI_z = scale(t2ISI),
         t2iga_z = scale(t2iga_flow),
         t2testo_z = scale(t2test_conc),
         t2dheas_z = scale(t2dheas_flow),
         t2cort_z = scale(t2cort_conc),
         t2crp_z = scale(t2crp_conc),
         t2timediff_z = scale(t2timediff),
         t3TB_z = scale(t3TB), 
         t3EXH_z = scale(t3EXH),
         t3DEV_z = scale(t3DEV),
         t3RSA_z = scale(t3RSA),
         t3PS_z = scale(t3PS),
         t3DS_z = scale(t3DS),
         t3PSQI_z = scale(t3PSQI),
         t3ISI_z = scale(t3ISI),
         t3iga_z = scale(t3iga_flow),
         t3testo_z = scale(t3test_conc),
         t3dheas_z = scale(t3dheas_flow),
         t3cort_z = scale(t3cort_conc),
         t3crp_z = scale(t3crp_conc),
         t3timediff_z = scale(t3timediff))

##replacing extremes with NAs
#wave 1
datz$t1TB <- replace(datz$t1TB, abs(datz$t1TB_z) > 3.29, NA)
datz$t1EXH <- replace(datz$t1EXH, abs(datz$t1EXH_z) > 3.29, NA)
datz$t1DEV <- replace(datz$t1DEV, abs(datz$t1DEV_z) > 3.29, NA)
datz$t1RSA <- replace(datz$t1RSA, abs(datz$t1RSA_z) > 3.29, NA)
datz$t1PS <- replace(datz$t1PS, abs(datz$t1PS_z) > 3.29, NA)
datz$t1DS <- replace(datz$t1DS, abs(datz$t1DS_z) > 3.29, NA)
datz$t1PSQI <- replace(datz$t1PSQI, abs(datz$t1PSQI_z) > 3.29, NA)
datz$t1ISI <- replace(datz$t1ISI, abs(datz$t1ISI_z) > 3.29, NA)
datz$t1iga_flow <- replace(datz$t1iga_flow, abs(datz$t1iga_z) > 3.29, NA)
datz$t1test_conc <- replace(datz$t1test_conc, abs(datz$t1testo_z) > 3.29, NA)
datz$t1dheas_flow <- replace(datz$t1dheas_flow, abs(datz$t1dheas_z) > 3.29, NA)
datz$t1cort_conc <- replace(datz$t1cort_conc, abs(datz$t1cort_z) > 3.29, NA)
datz$t1crp_conc <- replace(datz$t1crp_conc, abs(datz$t1crp_z) > 3.29, NA)

##wave1 for z-values
datz$t1TB_z <- replace(datz$t1TB_z, abs(datz$t1TB_z) > 3.29, NA)
datz$t1EXH_z <- replace(datz$t1EXH_z, abs(datz$t1EXH_z) > 3.29, NA)
datz$t1DEV_z <- replace(datz$t1DEV_z, abs(datz$t1DEV_z) > 3.29, NA)
datz$t1RSA_z <- replace(datz$t1RSA_z, abs(datz$t1RSA_z) > 3.29, NA)
datz$t1PS_z <- replace(datz$t1PS_z, abs(datz$t1PS_z) > 3.29, NA)
datz$t1DS_z <- replace(datz$t1DS_z, abs(datz$t1DS_z) > 3.29, NA)
datz$t1PSQI_z <- replace(datz$t1PSQI_z, abs(datz$t1PSQI_z) > 3.29, NA)
datz$t1ISI_z <- replace(datz$t1ISI_z, abs(datz$t1ISI_z) > 3.29, NA)
datz$t1iga_z <- replace(datz$t1iga_z, abs(datz$t1iga_z) > 3.29, NA)
datz$t1testo_z <- replace(datz$t1testo_z, abs(datz$t1testo_z) > 3.29, NA)
datz$t1dheas_z <- replace(datz$t1dheas_z, abs(datz$t1dheas_z) > 3.29, NA)
datz$t1cort_z <- replace(datz$t1cort_z, abs(datz$t1cort_z) > 3.29, NA)
datz$t1crp_z <- replace(datz$t1crp_z, abs(datz$t1crp_z) > 3.29, NA)

#wave 2
datz$t2TB <- replace(datz$t2TB, abs(datz$t2TB_z) > 3.29, NA)
datz$t2EXH <- replace(datz$t2EXH, abs(datz$t2EXH_z) > 3.29, NA)
datz$t2DEV <- replace(datz$t2DEV, abs(datz$t2DEV_z) > 3.29, NA)
datz$t2RSA <- replace(datz$t2RSA, abs(datz$t2RSA_z) > 3.29, NA)
datz$t2PS <- replace(datz$t2PS, abs(datz$t2PS_z) > 3.29, NA)
datz$t2DS <- replace(datz$t2DS, abs(datz$t2DS_z) > 3.29, NA)
datz$t2PSQI <- replace(datz$t2PSQI, abs(datz$t2PSQI_z) > 3.29, NA)
datz$t2ISI <- replace(datz$t2ISI, abs(datz$t2ISI_z) > 3.29, NA)
datz$t2iga_flow <- replace(datz$t2iga_flow, abs(datz$t2iga_z) > 3.29, NA)
datz$t2test_conc <- replace(datz$t2test_conc, abs(datz$t2testo_z) > 3.29, NA)
datz$t2dheas_flow <- replace(datz$t2dheas_flow, abs(datz$t2dheas_z) > 3.29, NA)
datz$t2cort_conc <- replace(datz$t2cort_conc, abs(datz$t2cort_z) > 3.29, NA)
datz$t2crp_conc <- replace(datz$t2crp_conc, abs(datz$t2crp_z) > 3.29, NA)

##wave2 for z-values
datz$t2TB_z <- replace(datz$t2TB_z, abs(datz$t2TB_z) > 3.29, NA)
datz$t2EXH_z <- replace(datz$t2EXH_z, abs(datz$t2EXH_z) > 3.29, NA)
datz$t2DEV_z <- replace(datz$t2DEV_z, abs(datz$t2DEV_z) > 3.29, NA)
datz$t2RSA_z <- replace(datz$t2RSA_z, abs(datz$t2RSA_z) > 3.29, NA)
datz$t2PS_z <- replace(datz$t2PS_z, abs(datz$t2PS_z) > 3.29, NA)
datz$t2DS_z <- replace(datz$t2DS_z, abs(datz$t2DS_z) > 3.29, NA)
datz$t2PSQI_z <- replace(datz$t2PSQI_z, abs(datz$t2PSQI_z) > 3.29, NA)
datz$t2ISI_z <- replace(datz$t2ISI_z, abs(datz$t2ISI_z) > 3.29, NA)
datz$t2iga_z <- replace(datz$t2iga_z, abs(datz$t2iga_z) > 3.29, NA)
datz$t2testo_z <- replace(datz$t2testo_z, abs(datz$t2testo_z) > 3.29, NA)
datz$t2dheas_z <- replace(datz$t2dheas_z, abs(datz$t2dheas_z) > 3.29, NA)
datz$t2cort_z <- replace(datz$t2cort_z, abs(datz$t2cort_z) > 3.29, NA)
datz$t2crp_z <- replace(datz$t2crp_z, abs(datz$t2crp_z) > 3.29, NA)

#wave 3
datz$t3TB <- replace(datz$t3TB, abs(datz$t3TB_z) > 3.29, NA)
datz$t3EXH <- replace(datz$t3EXH, abs(datz$t3EXH_z) > 3.29, NA)
datz$t3DEV <- replace(datz$t3DEV, abs(datz$t3DEV_z) > 3.29, NA)
datz$t3RSA <- replace(datz$t3RSA, abs(datz$t3RSA_z) > 3.29, NA)
datz$t3PS <- replace(datz$t3PS, abs(datz$t3PS_z) > 3.29, NA)
datz$t3DS <- replace(datz$t3DS, abs(datz$t3DS_z) > 3.29, NA)
datz$t3PSQI <- replace(datz$t3PSQI, abs(datz$t3PSQI_z) > 3.29, NA)
datz$t3ISI <- replace(datz$t3ISI, abs(datz$t3ISI_z) > 3.29, NA)
datz$t3iga_flow <- replace(datz$t3iga_flow, abs(datz$t3iga_z) > 3.29, NA)
datz$t3test_conc <- replace(datz$t3test_conc, abs(datz$t3testo_z) > 3.29, NA)
datz$t3dheas_flow <- replace(datz$t3dheas_flow, abs(datz$t3dheas_z) > 3.29, NA)
datz$t3cort_conc <- replace(datz$t3cort_conc, abs(datz$t3cort_z) > 3.29, NA)
datz$t3crp_conc <- replace(datz$t3crp_conc, abs(datz$t3crp_z) > 3.29, NA)

##wave3 for z-values
datz$t3TB_z <- replace(datz$t3TB_z, abs(datz$t3TB_z) > 3.29, NA)
datz$t3EXH_z <- replace(datz$t3EXH_z, abs(datz$t3EXH_z) > 3.29, NA)
datz$t3DEV_z <- replace(datz$t3DEV_z, abs(datz$t3DEV_z) > 3.29, NA)
datz$t3RSA_z <- replace(datz$t3RSA_z, abs(datz$t3RSA_z) > 3.29, NA)
datz$t3PS_z <- replace(datz$t3PS_z, abs(datz$t3PS_z) > 3.29, NA)
datz$t3DS_z <- replace(datz$t3DS_z, abs(datz$t3DS_z) > 3.29, NA)
datz$t3PSQI_z <- replace(datz$t3PSQI_z, abs(datz$t3PSQI_z) > 3.29, NA)
datz$t3ISI_z <- replace(datz$t3ISI_z, abs(datz$t3ISI_z) > 3.29, NA)
datz$t3iga_z <- replace(datz$t3iga_z, abs(datz$t3iga_z) > 3.29, NA)
datz$t3testo_z <- replace(datz$t3testo_z, abs(datz$t3testo_z) > 3.29, NA)
datz$t3dheas_z <- replace(datz$t3dheas_z, abs(datz$t3dheas_z) > 3.29, NA)
datz$t3cort_z <- replace(datz$t3cort_z, abs(datz$t3cort_z) > 3.29, NA)
datz$t3crp_z <- replace(datz$t3crp_z, abs(datz$t3crp_z) > 3.29, NA)
```

# Creating a long format
```{r reformating}
#total burnout
datl_tb <- datz %>% 
  dplyr::select(sample_id, t1TB, t2TB, t3TB) %>%
  pivot_longer(cols = c(t1TB, t2TB, t3TB),
                               names_to = "timepoint",
                               values_to = "TB") %>%
  mutate(timepoint = case_when(timepoint== "t1TB" ~"t1", 
                         timepoint =="t2TB" ~ "t2",
                         timepoint =="t3TB" ~ "t3"))
datl_tbz <- datz %>% 
  dplyr::select(sample_id, t1TB_z, t2TB_z, t3TB_z) %>%
  pivot_longer(cols = c(t1TB_z, t2TB_z, t3TB_z),
                               names_to = "timepoint",
                               values_to = "TBz") %>%
  mutate(timepoint = case_when(timepoint== "t1TB_z" ~"t1", 
                         timepoint =="t2TB_z" ~ "t2",
                         timepoint =="t3TB_z" ~ "t3"))
#exhaustion
datl_exh <- datz %>% 
  dplyr::select(sample_id, t1EXH, t2EXH, t3EXH) %>%
  pivot_longer(cols = c(t1EXH, t2EXH, t3EXH),
                               names_to = "timepoint",
                               values_to = "EXH") %>%
  mutate(timepoint = case_when(timepoint== "t1EXH" ~"t1", 
                         timepoint =="t2EXH" ~ "t2",
                         timepoint =="t3EXH" ~ "t3"))
datl_exhz <- datz %>% 
  dplyr::select(sample_id, t1EXH_z, t2EXH_z, t3EXH_z) %>%
  pivot_longer(cols = c(t1EXH_z, t2EXH_z, t3EXH_z),
                               names_to = "timepoint",
                               values_to = "EXHz") %>%
  mutate(timepoint = case_when(timepoint== "t1EXH_z" ~"t1", 
                         timepoint =="t2EXH_z" ~ "t2",
                         timepoint =="t3EXH_z" ~ "t3"))
#devaluation
datl_dev <- datz %>% 
  dplyr::select(sample_id, t1DEV, t2DEV, t3DEV) %>%
  pivot_longer(cols = c(t1DEV, t2DEV, t3DEV),
                               names_to = "timepoint",
                               values_to = "DEV") %>%
  mutate(timepoint = case_when(timepoint== "t1DEV" ~"t1", 
                         timepoint =="t2DEV" ~ "t2",
                         timepoint =="t3DEV" ~ "t3"))
datl_devz <- datz %>% 
  dplyr::select(sample_id, t1DEV_z, t2DEV_z, t3DEV_z) %>%
  pivot_longer(cols = c(t1DEV_z, t2DEV_z, t3DEV_z),
                               names_to = "timepoint",
                               values_to = "DEVz") %>%
  mutate(timepoint = case_when(timepoint== "t1DEV_z" ~"t1", 
                         timepoint =="t2DEV_z" ~ "t2",
                         timepoint =="t3DEV_z" ~ "t3"))
#rsa
datl_rsa <- datz %>% 
  dplyr::select(sample_id, t1RSA, t2RSA, t3RSA) %>%
  pivot_longer(cols = c(t1RSA, t2RSA, t3RSA),
                               names_to = "timepoint",
                               values_to = "RSA") %>%
  mutate(timepoint = case_when(timepoint== "t1RSA" ~"t1", 
                         timepoint =="t2RSA" ~ "t2",
                         timepoint =="t3RSA" ~ "t3"))
datl_rsaz <- datz %>% 
  dplyr::select(sample_id, t1RSA_z, t2RSA_z, t3RSA_z) %>%
  pivot_longer(cols = c(t1RSA_z, t2RSA_z, t3RSA_z),
                               names_to = "timepoint",
                               values_to = "RSAz") %>%
  mutate(timepoint = case_when(timepoint== "t1RSA_z" ~"t1", 
                         timepoint =="t2RSA_z" ~ "t2",
                         timepoint =="t3RSA_z" ~ "t3"))
#DS
datl_ds <- datz %>% 
  dplyr::select(sample_id, t1DS, t2DS, t3DS) %>%
  pivot_longer(cols = c(t1DS, t2DS, t3DS),
                               names_to = "timepoint",
                               values_to = "DS") %>%
  mutate(timepoint = case_when(timepoint== "t1DS" ~"t1", 
                         timepoint =="t2DS" ~ "t2",
                         timepoint =="t3DS" ~ "t3"))
datl_dsz <- datz %>% 
  dplyr::select(sample_id, t1DS_z, t2DS_z, t3DS_z) %>%
  pivot_longer(cols = c(t1DS_z, t2DS_z, t3DS_z),
                               names_to = "timepoint",
                               values_to = "DSz") %>%
  mutate(timepoint = case_when(timepoint== "t1DS_z" ~"t1", 
                         timepoint =="t2DS_z" ~ "t2",
                         timepoint =="t3DS_z" ~ "t3"))
#PS
datl_ps <- datz %>% 
  dplyr::select(sample_id, t1PS, t2PS, t3PS) %>%
  pivot_longer(cols = c(t1PS, t2PS, t3PS),
                               names_to = "timepoint",
                               values_to = "PS") %>%
  mutate(timepoint = case_when(timepoint== "t1PS" ~"t1", 
                         timepoint =="t2PS" ~ "t2",
                         timepoint =="t3PS" ~ "t3"))
datl_psz <- datz %>% 
  dplyr::select(sample_id, t1PS_z, t2PS_z, t3PS_z) %>%
  pivot_longer(cols = c(t1PS_z, t2PS_z, t3PS_z),
                               names_to = "timepoint",
                               values_to = "PSz") %>%
  mutate(timepoint = case_when(timepoint== "t1PS_z" ~"t1", 
                         timepoint =="t2PS_z" ~ "t2",
                         timepoint =="t3PS_z" ~ "t3"))
#PSQI
datl_psqi <- datz %>% 
  dplyr::select(sample_id, t1PSQI, t2PSQI, t3PSQI) %>%
  pivot_longer(cols = c(t1PSQI, t2PSQI, t3PSQI),
                               names_to = "timepoint",
                               values_to = "PSQI") %>%
  mutate(timepoint = case_when(timepoint== "t1PSQI" ~"t1", 
                         timepoint =="t2PSQI" ~ "t2",
                         timepoint =="t3PSQI" ~ "t3"))
datl_psqiz <- datz %>% 
  dplyr::select(sample_id, t1PSQI_z, t2PSQI_z, t3PSQI_z) %>%
  pivot_longer(cols = c(t1PSQI_z, t2PSQI_z, t3PSQI_z),
                               names_to = "timepoint",
                               values_to = "PSQIz") %>%
  mutate(timepoint = case_when(timepoint== "t1PSQI_z" ~"t1", 
                         timepoint =="t2PSQI_z" ~ "t2",
                         timepoint =="t3PSQI_z" ~ "t3"))
#ISI
datl_isi <- datz %>% 
  dplyr::select(sample_id, t1ISI, t2ISI, t3ISI) %>%
  pivot_longer(cols = c(t1ISI, t2ISI, t3ISI),
                               names_to = "timepoint",
                               values_to = "ISI") %>%
  mutate(timepoint = case_when(timepoint== "t1ISI" ~"t1", 
                         timepoint =="t2ISI" ~ "t2",
                         timepoint =="t3ISI" ~ "t3"))
datl_isiz <- datz %>% 
  dplyr::select(sample_id, t1ISI_z, t2ISI_z, t3ISI_z) %>%
  pivot_longer(cols = c(t1ISI_z, t2ISI_z, t3ISI_z),
                               names_to = "timepoint",
                               values_to = "ISIz") %>%
  mutate(timepoint = case_when(timepoint== "t1ISI_z" ~"t1", 
                         timepoint =="t2ISI_z" ~ "t2",
                         timepoint =="t3ISI_z" ~ "t3"))
#iga flow
datl_igaflow <- datz %>% 
  dplyr::select(sample_id, t1iga_flow, t2iga_flow, t3iga_flow) %>%
  pivot_longer(cols = c(t1iga_flow, t2iga_flow, t3iga_flow),
                               names_to = "timepoint",
                               values_to = "iga_flow") %>%
  mutate(timepoint = case_when(timepoint== "t1iga_flow" ~"t1", 
                         timepoint =="t2iga_flow" ~ "t2",
                         timepoint =="t3iga_flow" ~ "t3"))
datl_igafz <- datz %>% 
  dplyr::select(sample_id, t1iga_z, t2iga_z, t3iga_z) %>%
  pivot_longer(cols = c(t1iga_z, t2iga_z, t3iga_z),
                               names_to = "timepoint",
                               values_to = "iga_flowz") %>%
  mutate(timepoint = case_when(timepoint== "t1iga_z" ~"t1", 
                         timepoint =="t2iga_z" ~ "t2",
                         timepoint =="t3iga_z" ~ "t3"))
#testosterone conc
datl_testc <- datz %>% 
  dplyr::select(sample_id, t1test_conc, t2test_conc, t3test_conc) %>%
  pivot_longer(cols = c(t1test_conc, t2test_conc, t3test_conc),
                               names_to = "timepoint",
                               values_to = "test_conc") %>%
  mutate(timepoint = case_when(timepoint== "t1test_conc" ~"t1", 
                         timepoint =="t2test_conc" ~ "t2",
                         timepoint =="t3test_conc" ~ "t3"))
datl_testcz <- datz %>% 
  dplyr::select(sample_id, t1testo_z, t2testo_z, t3testo_z) %>%
  pivot_longer(cols = c(t1testo_z, t2testo_z, t3testo_z),
                               names_to = "timepoint",
                               values_to = "test_concz") %>%
  mutate(timepoint = case_when(timepoint== "t1testo_z" ~"t1", 
                         timepoint =="t2testo_z" ~ "t2",
                         timepoint =="t3testo_z" ~ "t3"))
#dheas flow
datl_dheasf <- datz %>% 
  dplyr::select(sample_id, t1dheas_flow, t2dheas_flow, t3dheas_flow) %>%
  pivot_longer(cols = c(t1dheas_flow, t2dheas_flow, t3dheas_flow),
                               names_to = "timepoint",
                               values_to = "dheas_flow") %>%
  mutate(timepoint = case_when(timepoint== "t1dheas_flow" ~"t1", 
                         timepoint =="t2dheas_flow" ~ "t2",
                         timepoint =="t3dheas_flow" ~ "t3"))
datl_dheasfz <- datz %>% 
  dplyr::select(sample_id, t1dheas_z, t2dheas_z, t3dheas_z) %>%
  pivot_longer(cols = c(t1dheas_z, t2dheas_z, t3dheas_z),
                               names_to = "timepoint",
                               values_to = "dheas_flowz") %>%
  mutate(timepoint = case_when(timepoint== "t1dheas_z" ~"t1", 
                         timepoint =="t2dheas_z" ~ "t2",
                         timepoint =="t3dheas_z" ~ "t3"))
#cort conc
datl_cortc <- datz %>% 
  dplyr::select(sample_id, t1cort_conc, t2cort_conc, t3cort_conc) %>%
  pivot_longer(cols = c(t1cort_conc, t2cort_conc, t3cort_conc),
                               names_to = "timepoint",
                               values_to = "cort_conc") %>%
  mutate(timepoint = case_when(timepoint== "t1cort_conc" ~"t1", 
                         timepoint =="t2cort_conc" ~ "t2",
                         timepoint =="t3cort_conc" ~ "t3"))
datl_cortcz <- datz %>% 
  dplyr::select(sample_id, t1cort_z, t2cort_z, t3cort_z) %>%
  pivot_longer(cols = c(t1cort_z, t2cort_z, t3cort_z),
                               names_to = "timepoint",
                               values_to = "cort_concz") %>%
  mutate(timepoint = case_when(timepoint== "t1cort_z" ~"t1", 
                         timepoint =="t2cort_z" ~ "t2",
                         timepoint =="t3cort_z" ~ "t3"))
#crp conc
datl_crpc <- datz %>% 
  dplyr::select(sample_id, t1crp_conc, t2crp_conc, t3crp_conc) %>%
  pivot_longer(cols = c(t1crp_conc, t2crp_conc, t3crp_conc),
                               names_to = "timepoint",
                               values_to = "crp_conc") %>%
  mutate(timepoint = case_when(timepoint== "t1crp_conc" ~"t1", 
                         timepoint =="t2crp_conc" ~ "t2",
                         timepoint =="t3crp_conc" ~ "t3"))
datl_crpcz <- datz %>% 
  dplyr::select(sample_id, t1crp_z, t2crp_z, t3crp_z) %>%
  pivot_longer(cols = c(t1crp_z, t2crp_z, t3crp_z),
                               names_to = "timepoint",
                               values_to = "crp_concz") %>%
  mutate(timepoint = case_when(timepoint== "t1crp_z" ~"t1", 
                         timepoint =="t2crp_z" ~ "t2",
                         timepoint =="t3crp_z" ~ "t3"))
#time difference
datl_timed <- datz %>% 
  dplyr::select(sample_id, t1timediff, t2timediff, t3timediff) %>%
  pivot_longer(cols = c(t1timediff, t2timediff, t3timediff),
                               names_to = "timepoint",
                               values_to = "timediff") %>%
  mutate(timepoint = case_when(timepoint== "t1timediff" ~"t1", 
                         timepoint =="t2timediff" ~ "t2",
                         timepoint =="t3timediff" ~ "t3"))
datl_timedz <- datz %>% 
  dplyr::select(sample_id, t1timediff_z, t2timediff_z, t3timediff_z) %>%
  pivot_longer(cols = c(t1timediff_z, t2timediff_z, t3timediff_z),
                               names_to = "timepoint",
                               values_to = "timediffz") %>%
  mutate(timepoint = case_when(timepoint== "t1timediff_z" ~"t1", 
                         timepoint =="t2timediff_z" ~ "t2",
                         timepoint =="t3timediff_z" ~ "t3"))

##notes
datl_notes <- datz %>% 
  dplyr::select(sample_id, t1notes, t2notes, t3notes) %>%
  pivot_longer(cols = c(t1notes, t2notes, t3notes),
                               names_to = "timepoint",
                               values_to = "notes") %>%
  mutate(timepoint = case_when(timepoint== "t1notes" ~"t1", 
                         timepoint =="t2notes" ~ "t2",
                         timepoint =="t3notes" ~ "t3"))

##join all files together
datl <- inner_join(datl_tb, datl_tbz, by = c("sample_id", "timepoint")) %>%
  inner_join(datl_exh, by = c("sample_id", "timepoint")) %>%
  inner_join(datl_exhz, by = c("sample_id", "timepoint")) %>%
  inner_join(datl_dev, by = c("sample_id", "timepoint")) %>%
  inner_join(datl_devz, by = c("sample_id", "timepoint")) %>%
  inner_join(datl_rsa, by = c("sample_id", "timepoint")) %>%
  inner_join(datl_rsaz, by = c("sample_id", "timepoint")) %>%
  inner_join(datl_ds, by = c("sample_id", "timepoint")) %>%
  inner_join(datl_dsz, by = c("sample_id", "timepoint")) %>%
  inner_join(datl_ps, by = c("sample_id", "timepoint")) %>%
  inner_join(datl_psz, by = c("sample_id", "timepoint")) %>%
  inner_join(datl_psqi, by = c("sample_id", "timepoint"))%>%
  inner_join(datl_psqiz, by = c("sample_id", "timepoint"))%>%
  inner_join(datl_isi, by = c("sample_id", "timepoint"))%>%
  inner_join(datl_isiz, by = c("sample_id", "timepoint"))%>%
  inner_join(datl_igaflow, by = c("sample_id", "timepoint"))%>%
  inner_join(datl_igafz, by = c("sample_id", "timepoint")) %>%
  inner_join(datl_testc, by = c("sample_id", "timepoint")) %>%
  inner_join(datl_testcz, by = c("sample_id", "timepoint")) %>%
  inner_join(datl_dheasf, by = c("sample_id", "timepoint"))%>%
  inner_join(datl_dheasfz, by = c("sample_id", "timepoint"))%>%
  inner_join(datl_cortc, by = c("sample_id", "timepoint"))%>%
  inner_join(datl_cortcz, by = c("sample_id", "timepoint"))%>%
  inner_join(datl_crpc, by = c("sample_id", "timepoint"))%>%
  inner_join(datl_crpcz, by = c("sample_id", "timepoint"))%>%
  inner_join(datl_timed, by = c("sample_id", "timepoint"))%>%
  inner_join(datl_timedz, by = c("sample_id", "timepoint"))%>%
  inner_join(datl_notes, by = c("sample_id", "timepoint"))
```

# Data filtering prior to modelling
```{r filter}
##remove row 182 for eating
datlx <- datl[-182,]
##filtering data by timepoint
datlx <- datlx %>% filter(timediff > 1.5)
##remove participant 91 for injury
datlx <- datlx %>% filter(sample_id != 91)
```

# Data imputation with MICE
The Bayesian estimator in lavaan does not have a way to estimate missing values, so missing values need to be imputed prior to analysis. Here, the mice package is used for imputation. 
```{r data imputation}
md.pattern(datlx)
datlxsub <- datlx %>% dplyr::select(sample_id, TBz, EXHz, DEVz, RSAz, 
                                    iga_flowz, test_concz, dheas_flowz, cort_concz, crp_concz, 
                                    PS, DS, ISI, PSQI, PSz, DSz, ISIz, PSQIz) %>%
  mutate(TBz = as.vector(TBz),
         EXHz = as.vector(EXHz),
         DEVz = as.vector(DEVz),
         RSAz = as.vector(RSAz),
         iga_flowz = as.vector(iga_flowz),
         test_concz = as.vector(test_concz),
         dheas_flowz = as.vector(dheas_flowz),
         cort_concz = as.vector(cort_concz),
         crp_concz = as.vector(crp_concz),
         PSz = as.vector(PSz),
         DSz = as.vector(DSz),
         ISIz = as.vector(ISIz),
         PSQIz = as.vector(PSQIz))
datlxtp <- datlx %>% select(sample_id, timepoint, EXHz)

datlximp <- mice(datlxsub, method = "pmm", seed = 500)
summary(datlximp)
datlxcomb <- complete(datlximp)

datlx2 <- inner_join(datlxtp, datlxcomb) %>%
  mutate(EXHz = as.vector(EXHz))
```

# Determine SD for adjustment of priors to the data
Priors are based on previous research (and thus standardised betas), they need to be adjusted to the data in this study. To do so, SDs of the variables need to be calculated. 
```{r sds for prior adjustment}
datlx2 %>% summarise(mean(iga_flowz), mean(test_concz), mean(dheas_flowz), mean(cort_concz), mean(crp_concz),
                    mean(TBz), mean(EXHz), mean(DEVz), mean(RSAz), 
                    mean(PS), mean(DS), mean(ISI), mean(PSQI),
                    mean(PSz), mean(DSz), mean(ISIz), mean(PSQIz),
                    sd(iga_flowz), sd(test_concz), sd(dheas_flowz), sd(cort_concz), sd(crp_concz),
                    sd(TBz), sd(EXHz), sd(DEVz), sd(RSAz), 
                    sd(PS), sd(DS), sd(ISI), sd(PSQI),
                    sd(PSz), sd(DSz), sd(ISIz), sd(PSQIz))
```

# MLMs with Bayesian approach and all biomarkers (testosterone, DHEA-S, IgA) in one model
The models here align with the first models in the ML analysis where testosterone, DHEA-S, and IgA are used as simultaneous mediator. 
Two priors are being used. First, a model with no information priors (beta = 0, SD = 10) was fitted, then a model with priors based on previous research. 
```{r}
## PHYSICAL SYMPTOMS 
##TB x Biomarkers x PS
#WITHOUT PRIORS (/with no information priors)
tb_bio_ps2 <- '
level: within
iga_flowz ~ d1*TBz
test_concz ~ d2*TBz
dheas_flowz ~ d3*TBz
PS ~  f*TBz+e1*iga_flowz + e2*test_concz +e3*dheas_flowz 
de1:= d1*e1
de2:= d2*e2
de3:= d3*e3
totalw1 := de1+f
totalw2 := de2+f
totalw3 := de3+f

level: between
iga_flowz ~ a1*TBz
test_concz ~ a2*TBz
dheas_flowz ~ a3*TBz
PS ~ c*TBz +b1*iga_flowz + b2*test_concz + b3*dheas_flowz  
ab1:= a1*b1
ab2:= a2*b2
ab3:= a3*b3
totalb1 := ab1+c
totalb2 := ab2+c
totalb3 := ab3+c
'
bfittb_bio_ps2 <- bsem(model = tb_bio_ps2, data = datlx2, cluster = "sample_id", seed = 1)
summary(bfittb_bio_ps2, fit.measures = TRUE, standardized=TRUE)

# WITH PRIORS
tb_bio_ps1 <- '
level: within
iga_flowz ~ prior("normal(-0.35,0.1)")*TBz+d1*TBz
test_concz ~ prior("normal(-0.27,0.1)")*TBz+d2*TBz
dheas_flowz ~ prior("normal(-0.27,0.1)")*TBz+d3*TBz
PS ~ prior("normal(2.74,5)")*TBz + f*TBz+ prior("normal(0,10)")*iga_flowz+e1*iga_flowz + prior("normal(0,10)")*test_concz+ e2*test_concz + prior("normal(0,10)")*dheas_flowz+e3*dheas_flowz 
de1:= d1*e1
de2:= d2*e2
de3:= d3*e3
totalw1 := de1+f
totalw2 := de2+f
totalw3 := de3+f

level: between
iga_flowz ~ prior("normal(-0.09,0.2)")*TBz +a1*TBz
test_concz ~ prior("normal(0,1)")*TBz+a2*TBz
dheas_flowz ~ prior("normal(-0.09,0.2)")*TBz+a3*TBz
PS ~ prior("normal(5.48,5)")*TBz +c*TBz + prior("normal(0,10)")*iga_flowz+b1*iga_flowz + prior("normal(0,10)")*test_concz+ b2*test_concz + prior("normal(0.77,10)")*dheas_flowz+b3*dheas_flowz  
ab1:= a1*b1
ab2:= a2*b2
ab3:= a3*b3
totalb1 := ab1+c
totalb2 := ab2+c
totalb3 := ab3+c
'
bfittb_bio_ps1 <- bsem(model = tb_bio_ps1, data = datlx2, cluster = "sample_id", seed = 1)
summary(bfittb_bio_ps1, fit.measures = TRUE, standardized=TRUE)

##EXH x Biomarkers x PS
#WITHOUT PRIORS (/with no information priors)
exh_bio_ps2 <- '
level: within
iga_flowz ~ d1*EXHz
test_concz ~ d2*EXHz
dheas_flowz ~ d3*EXHz
PS ~  f*EXHz+e1*iga_flowz + e2*test_concz +e3*dheas_flowz 
de1:= d1*e1
de2:= d2*e2
de3:= d3*e3
totalw1 := de1+f
totalw2 := de2+f
totalw3 := de3+f

level: between
iga_flowz ~ a1*EXHz
test_concz ~ a2*EXHz
dheas_flowz ~ a3*EXHz
PS ~ c*EXHz +b1*iga_flowz + b2*test_concz + b3*dheas_flowz  
ab1:= a1*b1
ab2:= a2*b2
ab3:= a3*b3
totalb1 := ab1+c
totalb2 := ab2+c
totalb3 := ab3+c
'
bfitexh_bio_ps2 <- bsem(model = exh_bio_ps2, data = datlx2, cluster = "sample_id", sample = 5000, seed = 1)
summary(bfitexh_bio_ps2, fit.measures = TRUE, standardized=TRUE)

# WITH PRIORS
exh_bio_ps1 <- '
level: within
iga_flowz ~ prior("normal(-0.26,0.1)")*EXHz+d1*EXHz
test_concz ~ prior("normal(-0.27,0.1)")*EXHz+d2*EXHz
dheas_flowz ~ prior("normal(-0.04,0.1)")*EXHz+d3*EXHz
PS ~ prior("normal(2.66,5)")*EXHz + f*EXHz+ prior("normal(0,10)")*iga_flowz+e1*iga_flowz + prior("normal(0,10)")*test_concz+ e2*test_concz + prior("normal(0,10)")*dheas_flowz+e3*dheas_flowz 
de1:= d1*e1
de2:= d2*e2
de3:= d3*e3
totalw1 := de1+f
totalw2 := de2+f
totalw3 := de3+f

level: between
iga_flowz ~ prior("normal(-0.09,0.2)")*EXHz +a1*EXHz
test_concz ~ prior("normal(0,1)")*EXHz+a2*EXHz
dheas_flowz ~ prior("normal(0,1)")*EXHz+a3*EXHz
PS ~ prior("normal(5.32,5)")*EXHz +c*EXHz + prior("normal(0,10)")*iga_flowz+b1*iga_flowz + prior("normal(0,10)")*test_concz+ b2*test_concz + prior("normal(0.77,10)")*dheas_flowz+b3*dheas_flowz  
ab1:= a1*b1
ab2:= a2*b2
ab3:= a3*b3
totalb1 := ab1+c
totalb2 := ab2+c
totalb3 := ab3+c
'
bfitexh_bio_ps1 <- bsem(model = exh_bio_ps1, data = datlx2, cluster = "sample_id", sample = 5000, seed = 1)
summary(bfitexh_bio_ps1, fit.measures = TRUE, standardized=TRUE)

##DEV x Biomarkers x PS
#WITHOUT PRIORS (/with no information priors)
dev_bio_ps2 <- '
level: within
iga_flowz ~ d1*DEVz
test_concz ~ d2*DEVz
dheas_flowz ~ d3*DEVz
PS ~  f*DEVz+e1*iga_flowz + e2*test_concz +e3*dheas_flowz 
de1:= d1*e1
de2:= d2*e2
de3:= d3*e3
totalw1 := de1+f
totalw2 := de2+f
totalw3 := de3+f

level: between
iga_flowz ~ a1*DEVz
test_concz ~ a2*DEVz
dheas_flowz ~ a3*DEVz
PS ~ c*DEVz +b1*iga_flowz + b2*test_concz + b3*dheas_flowz  
ab1:= a1*b1
ab2:= a2*b2
ab3:= a3*b3
totalb1 := ab1+c
totalb2 := ab2+c
totalb3 := ab3+c
'
bfitdev_bio_ps2 <- bsem(model = dev_bio_ps2, data = datlx2, cluster = "sample_id", seed = 1)
summary(bfitdev_bio_ps2, fit.measures = TRUE, standardized=TRUE)

# WITH PRIORS
dev_bio_ps1 <- '
level: within
iga_flowz ~ prior("normal(-0.64,0.1)")*DEVz+d1*DEVz
test_concz ~ prior("normal(-0.1,0.1)")*DEVz+d2*DEVz
dheas_flowz ~ prior("normal(-0.28,0.1)")*DEVz+d3*DEVz
PS ~ prior("normal(1.41,5)")*DEVz + f*DEVz+ prior("normal(0,5)")*iga_flowz+e1*iga_flowz + prior("normal(0,5)")*test_concz+ e2*test_concz + prior("normal(0,5)")*dheas_flowz+e3*dheas_flowz 
de1:= d1*e1
de2:= d2*e2
de3:= d3*e3
totalw1 := de1+f
totalw2 := de2+f
totalw3 := de3+f

level: between
iga_flowz ~ prior("normal(-0.01,0.2)")*DEVz +a1*DEVz
test_concz ~ prior("normal(0,1)")*DEVz+a2*DEVz
dheas_flowz ~ prior("normal(0,1)")*DEVz+a3*DEVz
PS ~ prior("normal(4.23,5)")*DEVz +c*DEVz + prior("normal(0,5)")*iga_flowz+b1*iga_flowz + prior("normal(0,5)")*test_concz+ b2*test_concz + prior("normal(0.77,5)")*dheas_flowz+b3*dheas_flowz  
ab1:= a1*b1
ab2:= a2*b2
ab3:= a3*b3
totalb1 := ab1+c
totalb2 := ab2+c
totalb3 := ab3+c
'
bfitdev_bio_ps1 <- bsem(model = dev_bio_ps1, data = datlx2, cluster = "sample_id", seed = 1)
summary(bfitdev_bio_ps1, fit.measures = TRUE, standardized=TRUE)

##RSA x Biomarkers x PS
#WITHOUT PRIORS (/with no information priors)
rsa_bio_ps2 <- '
level: within
iga_flowz ~ d1*RSAz
test_concz ~ d2*RSAz
dheas_flowz ~ d3*RSAz
PS ~  f*RSAz+e1*iga_flowz + e2*test_concz +e3*dheas_flowz 
de1:= d1*e1
de2:= d2*e2
de3:= d3*e3
totalw1 := de1+f
totalw2 := de2+f
totalw3 := de3+f

level: between
iga_flowz ~ a1*RSAz
test_concz ~ a2*RSAz
dheas_flowz ~ a3*RSAz
PS ~ c*RSAz +b1*iga_flowz + b2*test_concz + b3*dheas_flowz  
ab1:= a1*b1
ab2:= a2*b2
ab3:= a3*b3
totalb1 := ab1+c
totalb2 := ab2+c
totalb3 := ab3+c
'
bfitrsa_bio_ps2 <- bsem(model = rsa_bio_ps2, data = datlx2, cluster = "sample_id", sample = 5000, seed = 1)
summary(bfitrsa_bio_ps2, fit.measures = TRUE, standardized=TRUE)

# WITH PRIORS
rsa_bio_ps1 <- '
level: within
iga_flowz ~ prior("normal(-0.1,0.2)")*RSAz+d1*RSAz
test_concz ~ prior("normal(-0.19,0.1)")*RSAz+d2*RSAz
dheas_flowz ~ prior("normal(-0.09,0.2)")*RSAz+d3*RSAz
PS ~ prior("normal(0.71,5)")*RSAz + f*RSAz+ prior("normal(0,5)")*iga_flowz+e1*iga_flowz + prior("normal(0,5)")*test_concz+ e2*test_concz + prior("normal(0,5)")*dheas_flowz+e3*dheas_flowz 
de1:= d1*e1
de2:= d2*e2
de3:= d3*e3
totalw1 := de1+f
totalw2 := de2+f
totalw3 := de3+f

level: between
iga_flowz ~ prior("normal(-0.1,0.5)")*RSAz +a1*RSAz
test_concz ~ prior("normal(-0.1,0.5)")*RSAz+a2*RSAz
dheas_flowz ~ prior("normal(0,1)")*RSAz+a3*RSAz
PS ~ prior("normal(4.28,5)")*RSAz +c*RSAz + prior("normal(0,5)")*iga_flowz+b1*iga_flowz + prior("normal(0,5)")*test_concz+ b2*test_concz + prior("normal(0.77,5)")*dheas_flowz+b3*dheas_flowz  
ab1:= a1*b1
ab2:= a2*b2
ab3:= a3*b3
totalb1 := ab1+c
totalb2 := ab2+c
totalb3 := ab3+c
'
bfitrsa_bio_ps1 <- bsem(model = rsa_bio_ps1, data = datlx2, cluster = "sample_id", sample = 5000, seed = 1)
summary(bfitrsa_bio_ps1, fit.measures = TRUE, standardized=TRUE)

## DEPRESSIVE SYMPTOMS
##TB x Biomarkers x DS
#WITHOUT PRIORS (/with no information priors)
tb_bio_ds2 <- '
level: within
iga_flowz ~ d1*TBz
test_concz ~ d2*TBz
dheas_flowz ~ d3*TBz
DS ~  f*TBz+e1*iga_flowz + e2*test_concz +e3*dheas_flowz 
de1:= d1*e1
de2:= d2*e2
de3:= d3*e3
totalw1 := de1+f
totalw2 := de2+f
totalw3 := de3+f

level: between
iga_flowz ~ a1*TBz
test_concz ~ a2*TBz
dheas_flowz ~ a3*TBz
DS ~ c*TBz +b1*iga_flowz + b2*test_concz + b3*dheas_flowz  
ab1:= a1*b1
ab2:= a2*b2
ab3:= a3*b3
totalb1 := ab1+c
totalb2 := ab2+c
totalb3 := ab3+c
'
bfittb_bio_ds2 <- bsem(model = tb_bio_ds2, data = datlx2, cluster = "sample_id", seed = 1)
summary(bfittb_bio_ds2, fit.measures = TRUE, standardized=TRUE)

# WITH PRIORS
tb_bio_ds1 <- '
level: within
iga_flowz ~ prior("normal(-0.35,0.1)")*TBz+d1*TBz
test_concz ~ prior("normal(-0.27,0.1)")*TBz+d2*TBz
dheas_flowz ~ prior("normal(-0.27,0.1)")*TBz+d3*TBz
DS ~ prior("normal(0.7,1)")*TBz + f*TBz+ prior("normal(0,5)")*iga_flowz+e1*iga_flowz + prior("normal(0,5)")*test_concz+ e2*test_concz + prior("normal(0,5)")*dheas_flowz+e3*dheas_flowz 
de1:= d1*e1
de2:= d2*e2
de3:= d3*e3
totalw1 := de1+f
totalw2 := de2+f
totalw3 := de3+f

level: between
iga_flowz ~ prior("normal(-0.09,0.2)")*TBz +a1*TBz
test_concz ~ prior("normal(0,1)")*TBz+a2*TBz
dheas_flowz ~ prior("normal(-0.09,0.2)")*TBz+a3*TBz
DS ~ prior("normal(2.79,5)")*TBz +c*TBz + prior("normal(-0.79,5)")*iga_flowz+b1*iga_flowz + prior("normal(-0.77,5)")*test_concz+ b2*test_concz + prior("normal(-0.78,5)")*dheas_flowz+b3*dheas_flowz  
ab1:= a1*b1
ab2:= a2*b2
ab3:= a3*b3
totalb1 := ab1+c
totalb2 := ab2+c
totalb3 := ab3+c
'
bfittb_bio_ds1 <- bsem(model = tb_bio_ds1, data = datlx2, cluster = "sample_id", seed = 1)
summary(bfittb_bio_ds1, fit.measures = TRUE, standardized=TRUE)

##EXH x Biomarkers x DS
#WITHOUT PRIORS (/with no information priors)
exh_bio_ds2 <- '
level: within
iga_flowz ~ d1*EXHz
test_concz ~ d2*EXHz
dheas_flowz ~ d3*EXHz
DS ~  f*EXHz+e1*iga_flowz + e2*test_concz +e3*dheas_flowz 
de1:= d1*e1
de2:= d2*e2
de3:= d3*e3
totalw1 := de1+f
totalw2 := de2+f
totalw3 := de3+f

level: between
iga_flowz ~ a1*EXHz
test_concz ~ a2*EXHz
dheas_flowz ~ a3*EXHz
DS ~ c*EXHz +b1*iga_flowz + b2*test_concz + b3*dheas_flowz  
ab1:= a1*b1
ab2:= a2*b2
ab3:= a3*b3
totalb1 := ab1+c
totalb2 := ab2+c
totalb3 := ab3+c
'
bfitexh_bio_ds2 <- bsem(model = exh_bio_ds2, data = datlx2, cluster = "sample_id", seed = 1)
summary(bfitexh_bio_ds2, fit.measures = TRUE, standardized=TRUE)

# WITH PRIORS
exh_bio_ds1 <- '
level: within
iga_flowz ~ prior("normal(-0.26,0.1)")*EXHz+d1*EXHz
test_concz ~ prior("normal(-0.27,0.1)")*EXHz+d2*EXHz
dheas_flowz ~ prior("normal(-0.04,0.1)")*EXHz+d3*EXHz
DS ~ prior("normal(1.16,1)")*EXHz + f*EXHz+ prior("normal(0,5)")*iga_flowz+e1*iga_flowz + prior("normal(0,5)")*test_concz+ e2*test_concz + prior("normal(0,5)")*dheas_flowz+e3*dheas_flowz 
de1:= d1*e1
de2:= d2*e2
de3:= d3*e3
totalw1 := de1+f
totalw2 := de2+f
totalw3 := de3+f

level: between
iga_flowz ~ prior("normal(-0.09,0.2)")*EXHz +a1*EXHz
test_concz ~ prior("normal(0,1)")*EXHz+a2*EXHz
dheas_flowz ~ prior("normal(0,1)")*EXHz+a3*EXHz
DS ~ prior("normal(1.36,5)")*EXHz +c*EXHz + prior("normal(-0.79,5)")*iga_flowz+b1*iga_flowz + prior("normal(-0.77,5)")*test_concz+ b2*test_concz + prior("normal(-0.78,5)")*dheas_flowz+b3*dheas_flowz  
ab1:= a1*b1
ab2:= a2*b2
ab3:= a3*b3
totalb1 := ab1+c
totalb2 := ab2+c
totalb3 := ab3+c
'
bfitexh_bio_ds1 <- bsem(model = exh_bio_ds1, data = datlx2, cluster = "sample_id", sample = 5000, seed = 1)
summary(bfitexh_bio_ds1, fit.measures = TRUE, standardized=TRUE)

##DEV x Biomarkers x DS
#WITHOUT PRIORS (/with no information priors)
dev_bio_ds2 <- '
level: within
iga_flowz ~ d1*DEVz
test_concz ~ d2*DEVz
dheas_flowz ~ d3*DEVz
DS ~  f*DEVz+e1*iga_flowz + e2*test_concz +e3*dheas_flowz 
de1:= d1*e1
de2:= d2*e2
de3:= d3*e3
totalw1 := de1+f
totalw2 := de2+f
totalw3 := de3+f

level: between
iga_flowz ~ a1*DEVz
test_concz ~ a2*DEVz
dheas_flowz ~ a3*DEVz
DS ~ c*DEVz +b1*iga_flowz + b2*test_concz + b3*dheas_flowz  
ab1:= a1*b1
ab2:= a2*b2
ab3:= a3*b3
totalb1 := ab1+c
totalb2 := ab2+c
totalb3 := ab3+c
'
bfitdev_bio_ds2 <- bsem(model = dev_bio_ds2, data = datlx2, cluster = "sample_id", seed = 1)
summary(bfitdev_bio_ds2, fit.measures = TRUE, standardized=TRUE)

# WITH PRIORS
dev_bio_ds1 <- '
level: within
iga_flowz ~ prior("normal(-0.64,0.1)")*DEVz+d1*DEVz
test_concz ~ prior("normal(-0.1,0.1)")*DEVz+d2*DEVz
dheas_flowz ~ prior("normal(-0.28,0.1)")*DEVz+d3*DEVz
DS ~ prior("normal(0.07,1)")*DEVz + f*DEVz+ prior("normal(0,5)")*iga_flowz+e1*iga_flowz + prior("normal(0,5)")*test_concz+ e2*test_concz + prior("normal(0,5)")*dheas_flowz+e3*dheas_flowz 
de1:= d1*e1
de2:= d2*e2
de3:= d3*e3
totalw1 := de1+f
totalw2 := de2+f
totalw3 := de3+f

level: between
iga_flowz ~ prior("normal(-0.01,0.2)")*DEVz +a1*DEVz
test_concz ~ prior("normal(0,1)")*DEVz+a2*DEVz
dheas_flowz ~ prior("normal(0,1)")*DEVz+a3*DEVz
DS ~ prior("normal(0.07,5)")*DEVz +c*DEVz + prior("normal(0.79,5)")*iga_flowz+b1*iga_flowz + prior("normal(-0.77,5)")*test_concz+ b2*test_concz + prior("normal(0.78,5)")*dheas_flowz+b3*dheas_flowz  
ab1:= a1*b1
ab2:= a2*b2
ab3:= a3*b3
totalb1 := ab1+c
totalb2 := ab2+c
totalb3 := ab3+c
'
bfitdev_bio_ds1 <- bsem(model = dev_bio_ds1, data = datlx2, cluster = "sample_id", seed = 1)
summary(bfitdev_bio_ds1, fit.measures = TRUE, standardized=TRUE)

##RSA x Biomarkers x DS
#WITHOUT PRIORS (/with no information priors)
rsa_bio_ds2 <- '
level: within
iga_flowz ~ d1*RSAz
test_concz ~ d2*RSAz
dheas_flowz ~ d3*RSAz
DS ~  f*RSAz+e1*iga_flowz + e2*test_concz +e3*dheas_flowz 
de1:= d1*e1
de2:= d2*e2
de3:= d3*e3
totalw1 := de1+f
totalw2 := de2+f
totalw3 := de3+f

level: between
iga_flowz ~ a1*RSAz
test_concz ~ a2*RSAz
dheas_flowz ~ a3*RSAz
DS ~ c*RSAz +b1*iga_flowz + b2*test_concz + b3*dheas_flowz  
ab1:= a1*b1
ab2:= a2*b2
ab3:= a3*b3
totalb1 := ab1+c
totalb2 := ab2+c
totalb3 := ab3+c
'
bfitrsa_bio_ds2 <- bsem(model = rsa_bio_ds2, data = datlx2, cluster = "sample_id", sample = 7500, seed = 1)
summary(bfitrsa_bio_ds2, fit.measures = TRUE, standardized=TRUE)

# WITH PRIORS
rsa_bio_ds1 <- '
level: within
iga_flowz ~ prior("normal(-0.1,0.2)")*RSAz+d1*RSAz
test_concz ~ prior("normal(-0.19,0.1)")*RSAz+d2*RSAz
dheas_flowz ~ prior("normal(-0.09,0.2)")*RSAz+d3*RSAz
DS ~ prior("normal(0.36,1)")*RSAz + f*RSAz+ prior("normal(-0.79,1)")*iga_flowz+e1*iga_flowz + prior("normal(-0.77,1)")*test_concz+ e2*test_concz + prior("normal(-0.78,1)")*dheas_flowz+e3*dheas_flowz 
de1:= d1*e1
de2:= d2*e2
de3:= d3*e3
totalw1 := de1+f
totalw2 := de2+f
totalw3 := de3+f

level: between
iga_flowz ~ prior("normal(0.1,0.5)")*RSAz +a1*RSAz
test_concz ~ prior("normal(0.1,0.5)")*RSAz+a2*RSAz
dheas_flowz ~ prior("normal(0,1)")*RSAz+a3*RSAz
DS ~ prior("normal(2.91,5)")*RSAz +c*RSAz + prior("normal(-0.79,5)")*iga_flowz+b1*iga_flowz + prior("normal(-0.77,5)")*test_concz+ b2*test_concz + prior("normal(-0.78,5)")*dheas_flowz+b3*dheas_flowz  
ab1:= a1*b1
ab2:= a2*b2
ab3:= a3*b3
totalb1 := ab1+c
totalb2 := ab2+c
totalb3 := ab3+c
'
bfitrsa_bio_ds1 <- bsem(model = rsa_bio_ds1, data = datlx2, cluster = "sample_id", sample = 5000, seed = 1)
summary(bfitrsa_bio_ds1, fit.measures = TRUE, standardized=TRUE)

## INSOMNIA SYMPTOMS
##TB x Biomarkers x ISI
#WITHOUT PRIORS (/with no information priors)
tb_bio_isi2 <- '
level: within
iga_flowz ~ d1*TBz
test_concz ~ d2*TBz
dheas_flowz ~ d3*TBz
ISI ~  f*TBz+e1*iga_flowz + e2*test_concz +e3*dheas_flowz 
de1:= d1*e1
de2:= d2*e2
de3:= d3*e3
totalw1 := de1+f
totalw2 := de2+f
totalw3 := de3+f

level: between
iga_flowz ~ a1*TBz
test_concz ~ a2*TBz
dheas_flowz ~ a3*TBz
ISI ~ c*TBz +b1*iga_flowz + b2*test_concz + b3*dheas_flowz  
ab1:= a1*b1
ab2:= a2*b2
ab3:= a3*b3
totalb1 := ab1+c
totalb2 := ab2+c
totalb3 := ab3+c
'
bfittb_bio_isi2 <- bsem(model = tb_bio_isi2, data = datlx2, cluster = "sample_id", seed = 1)
summary(bfittb_bio_isi2, fit.measures = TRUE, standardized=TRUE)

# WITH PRIORS
tb_bio_isi1 <- '
level: within
iga_flowz ~ prior("normal(-0.35,0.1)")*TBz+d1*TBz
test_concz ~ prior("normal(-0.27,0.1)")*TBz+d2*TBz
dheas_flowz ~ prior("normal(-0.27,0.1)")*TBz+d3*TBz
ISI ~ prior("normal(1.05,1)")*TBz + f*TBz+ prior("normal(0,1)")*iga_flowz+e1*iga_flowz + prior("normal(0,1)")*test_concz+ e2*test_concz + prior("normal(0,1)")*dheas_flowz+e3*dheas_flowz 
de1:= d1*e1
de2:= d2*e2
de3:= d3*e3
totalw1 := de1+f
totalw2 := de2+f
totalw3 := de3+f

level: between
iga_flowz ~ prior("normal(-0.09,0.2)")*TBz +a1*TBz
test_concz ~ prior("normal(0,1)")*TBz+a2*TBz
dheas_flowz ~ prior("normal(-0.09,0.2)")*TBz+a3*TBz
ISI ~ prior("normal(2.10,5)")*TBz +c*TBz + prior("normal(-1.79,5)")*iga_flowz+b1*iga_flowz + prior("normal(-0.58,5)")*test_concz+ b2*test_concz + prior("normal(-1.18,5)")*dheas_flowz+b3*dheas_flowz  
ab1:= a1*b1
ab2:= a2*b2
ab3:= a3*b3
totalb1 := ab1+c
totalb2 := ab2+c
totalb3 := ab3+c
'
bfittb_bio_isi1 <- bsem(model = tb_bio_isi1, data = datlx2, cluster = "sample_id", seed = 1)
summary(bfittb_bio_isi1, fit.measures = TRUE, standardized=TRUE)

##EXH x Biomarkers x ISI
#WITHOUT PRIORS (/with no information priors)
exh_bio_isi2 <- '
level: within
iga_flowz ~ d1*EXHz
test_concz ~ d2*EXHz
dheas_flowz ~ d3*EXHz
ISI ~  f*EXHz+e1*iga_flowz + e2*test_concz +e3*dheas_flowz 
de1:= d1*e1
de2:= d2*e2
de3:= d3*e3
totalw1 := de1+f
totalw2 := de2+f
totalw3 := de3+f

level: between
iga_flowz ~ a1*EXHz
test_concz ~ a2*EXHz
dheas_flowz ~ a3*EXHz
ISI ~ c*EXHz +b1*iga_flowz + b2*test_concz + b3*dheas_flowz  
ab1:= a1*b1
ab2:= a2*b2
ab3:= a3*b3
totalb1 := ab1+c
totalb2 := ab2+c
totalb3 := ab3+c
'
bfitexh_bio_isi2 <- bsem(model = exh_bio_isi2, data = datlx2, cluster = "sample_id", sample = 5000, seed = 1)
summary(bfitexh_bio_isi2, fit.measures = TRUE, standardized=TRUE)

# WITH PRIORS
exh_bio_isi1 <- '
level: within
iga_flowz ~ prior("normal(-0.26,0.1)")*EXHz+d1*EXHz
test_concz ~ prior("normal(-0.27,0.1)")*EXHz+d2*EXHz
dheas_flowz ~ prior("normal(-0.27,0.1)")*EXHz+d3*EXHz
ISI ~ prior("normal(1.02,1)")*EXHz + f*EXHz+ prior("normal(0,1)")*iga_flowz+e1*iga_flowz + prior("normal(0,1)")*test_concz+ e2*test_concz + prior("normal(0,1)")*dheas_flowz+e3*dheas_flowz 
de1:= d1*e1
de2:= d2*e2
de3:= d3*e3
totalw1 := de1+f
totalw2 := de2+f
totalw3 := de3+f

level: between
iga_flowz ~ prior("normal(-0.09,0.2)")*EXHz +a1*EXHz
test_concz ~ prior("normal(0,1)")*EXHz+a2*EXHz
dheas_flowz ~ prior("normal(0,1)")*EXHz+a3*EXHz
ISI ~ prior("normal(2.04,5)")*EXHz +c*EXHz + prior("normal(-1.79,5)")*iga_flowz+b1*iga_flowz + prior("normal(-0.58,5)")*test_concz+ b2*test_concz + prior("normal(-1.18,5)")*dheas_flowz+b3*dheas_flowz  
ab1:= a1*b1
ab2:= a2*b2
ab3:= a3*b3
totalb1 := ab1+c
totalb2 := ab2+c
totalb3 := ab3+c
'
bfitexh_bio_isi1 <- bsem(model = exh_bio_isi1, data = datlx2, cluster = "sample_id", seed = 1)
summary(bfitexh_bio_isi1, fit.measures = TRUE, standardized=TRUE)

##DEV x Biomarkers x ISI
#WITHOUT PRIORS (/with no information priors)
dev_bio_isi2 <- '
level: within
iga_flowz ~ d1*DEVz
test_concz ~ d2*DEVz
dheas_flowz ~ d3*DEVz
ISI ~  f*DEVz+e1*iga_flowz + e2*test_concz +e3*dheas_flowz 
de1:= d1*e1
de2:= d2*e2
de3:= d3*e3
totalw1 := de1+f
totalw2 := de2+f
totalw3 := de3+f

level: between
iga_flowz ~ a1*DEVz
test_concz ~ a2*DEVz
dheas_flowz ~ a3*DEVz
ISI ~ c*DEVz +b1*iga_flowz + b2*test_concz + b3*dheas_flowz  
ab1:= a1*b1
ab2:= a2*b2
ab3:= a3*b3
totalb1 := ab1+c
totalb2 := ab2+c
totalb3 := ab3+c
'
bfitdev_bio_isi2 <- bsem(model = dev_bio_isi2, data = datlx2, cluster = "sample_id", seed = 1)
summary(bfitdev_bio_isi2, fit.measures = TRUE, standardized=TRUE)

# WITH PRIORS
dev_bio_isi1 <- '
level: within
iga_flowz ~ prior("normal(-0.64,0.1)")*DEVz+d1*DEVz
test_concz ~ prior("normal(-0.1,0.1)")*DEVz+d2*DEVz
dheas_flowz ~ prior("normal(-0.28,0.1)")*DEVz+d3*DEVz
ISI ~ prior("normal(1.15,1)")*DEVz + f*DEVz+ prior("normal(0,1)")*iga_flowz+e1*iga_flowz + prior("normal(0,1)")*test_concz+ e2*test_concz + prior("normal(0,1)")*dheas_flowz+e3*dheas_flowz 
de1:= d1*e1
de2:= d2*e2
de3:= d3*e3
totalw1 := de1+f
totalw2 := de2+f
totalw3 := de3+f

level: between
iga_flowz ~ prior("normal(0.01,0.2)")*DEVz +a1*DEVz
test_concz ~ prior("normal(0,1)")*DEVz+a2*DEVz
dheas_flowz ~ prior("normal(0,1)")*DEVz+a3*DEVz
ISI ~ prior("normal(0.54,5)")*DEVz +c*DEVz + prior("normal(-1.79,5)")*iga_flowz+b1*iga_flowz + prior("normal(-0.58,5)")*test_concz+ b2*test_concz + prior("normal(-1.18,5)")*dheas_flowz+b3*dheas_flowz  
ab1:= a1*b1
ab2:= a2*b2
ab3:= a3*b3
totalb1 := ab1+c
totalb2 := ab2+c
totalb3 := ab3+c
'
bfitdev_bio_isi1 <- bsem(model = dev_bio_isi1, data = datlx2, cluster = "sample_id", seed = 1)
summary(bfitdev_bio_isi1, fit.measures = TRUE, standardized=TRUE)

##RSA x Biomarkers x ISI
#WITHOUT PRIORS (/with no information priors)
rsa_bio_isi2 <- '
level: within
iga_flowz ~ d1*RSAz
test_concz ~ d2*RSAz
dheas_flowz ~ d3*RSAz
ISI ~  f*RSAz+e1*iga_flowz + e2*test_concz +e3*dheas_flowz 
de1:= d1*e1
de2:= d2*e2
de3:= d3*e3
totalw1 := de1+f
totalw2 := de2+f
totalw3 := de3+f

level: between
iga_flowz ~ a1*RSAz
test_concz ~ a2*RSAz
dheas_flowz ~ a3*RSAz
ISI ~ c*RSAz +b1*iga_flowz + b2*test_concz + b3*dheas_flowz  
ab1:= a1*b1
ab2:= a2*b2
ab3:= a3*b3
totalb1 := ab1+c
totalb2 := ab2+c
totalb3 := ab3+c
'
bfitrsa_bio_isi2 <- bsem(model = rsa_bio_isi2, data = datlx2, cluster = "sample_id", sample = 5000, seed = 1)
summary(bfitrsa_bio_isi2, fit.measures = TRUE, standardized=TRUE)

# WITH PRIORS
rsa_bio_isi1 <- '
level: within
iga_flowz ~ prior("normal(-0.1,0.2)")*RSAz+d1*RSAz
test_concz ~ prior("normal(-0.19,0.1)")*RSAz+d2*RSAz
dheas_flowz ~ prior("normal(-0.09,0.2)")*RSAz+d3*RSAz
ISI ~ prior("normal(0.27,1)")*RSAz + f*RSAz+ prior("normal(0,1)")*iga_flowz+e1*iga_flowz + prior("normal(0,1)")*test_concz+ e2*test_concz + prior("normal(0,1)")*dheas_flowz+e3*dheas_flowz 
de1:= d1*e1
de2:= d2*e2
de3:= d3*e3
totalw1 := de1+f
totalw2 := de2+f
totalw3 := de3+f

level: between
iga_flowz ~ prior("normal(0.1,0.5)")*RSAz +a1*RSAz
test_concz ~ prior("normal(0.1,0.5)")*RSAz+a2*RSAz
dheas_flowz ~ prior("normal(0,1)")*RSAz+a3*RSAz
ISI ~ prior("normal(1.64,5)")*RSAz +c*RSAz + prior("normal(-1.79,5)")*iga_flowz+b1*iga_flowz + prior("normal(-0.58,5)")*test_concz+ b2*test_concz + prior("normal(-1.18,5)")*dheas_flowz+b3*dheas_flowz  
ab1:= a1*b1
ab2:= a2*b2
ab3:= a3*b3
totalb1 := ab1+c
totalb2 := ab2+c
totalb3 := ab3+c
'
bfitrsa_bio_isi1 <- bsem(model = rsa_bio_isi1, data = datlx2, cluster = "sample_id", sample = 5000, seed = 1)
summary(bfitrsa_bio_isi1, fit.measures = TRUE, standardized=TRUE)
```